---
title: "Assigment 1"
author: "Isabel Zayas Rivera"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output: html_document
---


## Assigning Values

#### Q1. Create an object called height with the value 175.

```{r}
height <- 175
```


## Simple Math

#### Q.2 Calculate the result of 25 * 4 - 10.
```{r}
25 * 4 - 10
```
## Using Functions

#### Q. 3 Use the function sqrt() to calculate the square root of 81.

```{r}
sqrt(81)
```

## Character Objects

#### Q.4 Assign the phrase “R is fun!” to an object called message. 

```{r}
message <- "R is fun!"
print(message)
```

## Object Manipulation

#### Q.5 Create two objects a <- 10 and b <- 5. Calculate their sum and store it in c.

```{r}
a <- 10
b <- 5
c <- a + b 
```
```{r}
print(c)
```

## Logical Comparison 

#### Q.Test whether 15 is greater than 20.

```{r}
15 > 20
```

## Checking Classes

#### Q.7 Check the class of the object "Hello World".

```{r}
class("Hello World")
```

## Code Chunk Option 

#### Q.8 Run the following code chunk, observe the warnings that appear, and modify the chunk options to suppress warnings without changing the code itself.

```{r}
log(-1)
```

```{r, warning=FALSE}
log(-1)
```

#### Q.9 Run the following code chunk, observe the warnings that appear, and modify the chunk options to suppress warnings without changing the code itself.

```{r}
library(dplyr)
```

```{r, message=FALSE}
# Load a package (may produce a message)
library(dplyr)
```

## Creating and Analyzing a Vector

#### Q.10 Create a numeric vector called grades containing the values 80, 90, 75, 95, and 85. Then, use the mean() function to calculate the average grade and store the result in an object called average.


```{r}
grades <- c(80, 90, 75, 95, 85)
average <- mean(grades)
print(average)
```


