---
title: "Assigment 2"
author: "Isabel Zayas Rivera"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output: html_document
---

```{r}
library(ggplot2)
data("trees")
head(trees)
```


#### Q.1 Create a histogram showing the distribution of Girth.

```{r}
library(ggplot2)

ggplot(trees, aes(x = Girth)) +
  geom_histogram(binwidth= 2, fill = "pink", color = "white") +
  labs(
    title = "Distribution of Tree Girth",
    x = "Girth",
  ) +
  theme_classic()
  
```


#### Q.2 Create a histogram showing the distribution of Volume.


```{r}
ggplot(trees, aes(x = Volume)) +
  geom_histogram(binwidth= 2, fill = "lightblue", color = "white") +
  labs(
    title = "Distribution of Tree Volume",
    x = "Volume",
  ) +
  theme_classic()
```

#### Q.3 Create a scatterplot showing the relationship between Girth and Volume.

```{r}
ggplot(data = trees, aes(x= Girth, y= Volume)) +
  geom_point(color= "red") +
  labs(
    title = "Relationship between Girth and Volume",
    x= "Girth",
    y= "Volume"
  ) +
  theme_classic()
```

#### Q.4 Use the Shapiro–Wilk test to assess whether Volume is normally distributed. Report the p-value and state whether the data are normally distributed.

```{r}
shapiro.test(trees$Volume)

# There is a significant difference in the values 
```

#### Q.5 Repeat the Shapiro–Wilk test for Girth. Report the p-value and state whether Girth is normally distributed.

```{r}
shapiro.test(trees$Girth)

# There is no significant difference in the values
```









